---
title: "Field data summary"
author: "Brad Compton"
date: "`r timestamp <- lubridate::stamp('February 4, 2025', quiet = TRUE); timestamp(lubridate::now(tz = 'America/New_York'))`"
output: html_document
---
<style>
/* Limit body text width, center paragraphs and lists */
.main-container p,
.main-container ul,
.main-container ol,
.main-container blockquote {
max-width: 850px;
margin-left: auto;
margin-right: auto;
}

/* Do NOT constrain code output or code blocks */
.main-container pre,
.main-container pre.r,
.main-container code,
.main-container .r-output {
max-width: none !important;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA)
options(width = 150)

library(marshmap)
```

### Field data goals for U-Net
- Preliminary estimate is that we'll need >10k cells per subclass in a single year for robust fits
- We're cross-validating by holding out entire polygons (transects, MUs, or polys) for validation. For the years we model, we'll 
  need at least 10 (preferably more) polys per subclass in a single year. These should be scattered across the site, separated
  by >20 m or so, and ideally spanning the entire study area.
- Some subclasses are rare in some or all sites. We'll have to drop these as necessary because of insufficient sample sizes. For 
  preliminary fitting, we can just drop them, but when producing maps, we'll need to lump them so they map reasonably.
- Some subclasses are highly emphemeral, especially 32 (wrack). We may need to drop these. They'll present problems for mapping if we do.
- We obviously can't do much with data previously collected in the field at this point, but should be able to do PI for the classes
  where that's possible to fill out sampling requriements.
- Because marshes change over time, we'll want to pick a single year of field data and match orthos to it (within a year or so), 
  so we're looking for our minimum cell and poly requirements for single years.
- Some sites (OTH, ESS, others?) have had significant remediation efforts coinciding with our study, so we may not be able to model 
  for these sites. If we can find out dates that work was done, we may be able to work around it (e.g., if management started in 2022,
  we could use 2018-2021 data).
- For U-Net modeling, I'm going to pick a couple of sites and years to start with. We'll need strong data for those years, beefing up 
  PI where necessary and possible.

### Still needed
- Not all sites have been completed for 2025 (still missing ESS, BAR, and WES)
- Sites and years that don't have adequate orthos within a year or so aren't worth our effort.
- We still need the `year` and `targetyear` fields for both field and PI data at most sites. Note the `0` year in tables below.
- It's possible we could correct for insufficient polygons by breaking long field transects into separate polygons, but we'd probably
  have to delete ~20 m sections to avoid contaminating validation sets. I may be able to do this in code on the fly.
  
### Questions
- I still don't have 2023 orthos, so I don't know what we've got yet. They match a good field year.
- Were orthos flown in 2024?
- Could we fit 2023 field work from 2026 orthos? Unclear that we'll have the resources to fly these sites next summer, but perhaps
  we could target a promising site or two.



# OTH (Old Town Hill)

```{r}
fieldinfo('oth')
```

### Notes
- Active management at this site
- Have years for field and PI data, but missing for subclasses 1, 3, 9, 12 (are these all really possible from PI?!)
- 2018 and 2021 look reasonably promising (except for mowing in the high marsh). 2025 has a decent sample, but is 
  inadequate orthos.


# PEG (Peggotty Beach)

```{r}
fieldinfo('peg')
```

### Notes
- Unclear how promising this site is until we have dates


# SOR (South River)

```{r}
fieldinfo('sor')
```

### Notes
- Unclear how promising this site is until we have dates

# NOR (North River)

```{r}
fieldinfo('nor')
```

### Notes
- We have a crazy amount of data for 2019, 2023, and 2025 at this site (but insufficient orthos for 2025).


# WEL (Wellfleet Bay)

```{r}
fieldinfo('wel')
```

### Notes
- This site looks great for 2019, and perhaps promising for 2025 (though no orthos). Inadequate for 2023.


# RR (Red River)

```{r}
fieldinfo('rr')
```

### Notes
- Maybe 2019. 

# ESS (Essex Bay)

```{r}
#fieldinfo('ess')
```

### Notes
- Active management at this site
- No field data yet


# BAR (Barnstable)

```{r}
#fieldinfo('bar')
```

### Notes
- No field data yet


# WES (Westport)

```{r}
#fieldinfo('wes')
```

### Notes
- No field data yet






