---
# This newer version works on the single .gpkg field data file (fall 2026), using fieldinfo(..., onefile = TRUE)
title: "Field data summary"
subtitle: "UMass MassMarsh UAS project"
author: "Brad Compton"
date: "`r timestamp <- lubridate::stamp('February 4, 2025', quiet = TRUE); timestamp(lubridate::now(tz = 'America/New_York'))`"
output: html_document
---
<style>
/* Limit body text width, center paragraphs and lists */
.main-container p,
.main-container ul,
.main-container ol,
.main-container blockquote {
max-width: 850px;
margin-left: auto;
margin-right: auto;
}

/* Do NOT constrain code output or code blocks */
.main-container pre,
.main-container pre.r,
.main-container code,
.main-container .r-output {
max-width: none !important;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA)
options(width = 150)

library(marshmap)
```

<!---
##### Links
- this document: [https://landeco.umass.edu/web/massmarsh/field_data_summary.html](https://landeco.umass.edu/web/massmarsh/field_data_summary.html)
- Flight data summary: [https://landeco.umass.edu/web/massmarsh/flight_data_summary.html](https://landeco.umass.edu/web/massmarsh/flight_data_summary.html)
-->

### New version (September 2026)
This version brings in the new GeoPackage created by Rahim Mian (1 Sep 2026). This version incorporates data edits and uses
code to produce a single .gpkg. MUs and Transects are represented as points and lines, so need to be filled out:

- MU points are buffered 1 m, to produce a 2 m diameter circle
- Transect lines are clipped back 1 m at each end (collapsing to a point for lines <2 m), then buffered 1 m, such that
  the final transect polygons are 2 m wide with rounded ends that extend to the length of the line (except for lines <2 m).
  This better represents the field transects than the old approach, which did square buffers that extended the lines 1 m
  at each end.

#### Notes
- Number of cells are estimated based on dividing the polygons by 8 cm cells, so it won't be exact. These estimates 
  don't drop overlaps.
- The PI-based water polygons that Angel did in late 2025 have been dropped.

#### Fall 2026 modeling plans
- Reassess orthophoto availability (as there are additional orthos since Jan 2026)
- Select 5 sites for EPA report. Pick the ones with the best-looking data, preferring sites with processed hydro.
- Use U-Net to run the `primary` model for each, combining all years of field data and selecting solid orthos as close to
  the middle years (2021 or 2022) as possible.
- Make a map for each (as .png with legend, scalebar, and locator)
- Create water samples from high-tide NIR threshold, sampling random points with MU clipped to NIR threshold.


# OTH (Old Town Hill)

```{r}
fieldinfo('oth')
```

### Notes
- Active management at this site
- The large number of polygons for Year 0 subclasses 1, 3, 9, 12 have been dropped. What was their source? Were they Ryan's PI?


# PEG (Peggotty Beach)

```{r}
fieldinfo('peg')
```

### Notes


# SOR (South River)

```{r}
fieldinfo('sor')
```

### Notes


# NOR (North River)

```{r}
fieldinfo('nor')
```

### Notes


# WEL (Wellfleet Bay)

```{r}
fieldinfo('wel')
```

### Notes




# RR (Red River)

```{r}
fieldinfo('rr')
```

### Notes


# ESS (Essex Bay)

```{r}
fieldinfo('ess')
```

### Notes
- Active management at this site


# BAR (Barnstable)

```{r}
fieldinfo('bar')
```

### Notes



# WES (Westport)

```{r}
fieldinfo('wes')
```

### Notes







