---
title: "Flight data summary"
subtitle: "UMass MassMarsh UAS project"
author: "Brad Compton"
date: "`r timestamp <- lubridate::stamp('February 4, 2025', quiet = TRUE); timestamp(lubridate::now(tz = 'America/New_York'))`"
output: html_document
---
<style>
.main-container p,
.main-container ul,
.main-container ol,
.main-container blockquote {
max-width: 850px;
margin-left: auto;
margin-right: auto;
}

/* Do NOT constrain code output or code blocks */
.main-container pre,
.main-container pre.r,
.main-container code,
.main-container .r-output {
max-width: none !important;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA)
options(width = 150)

library(marshmap)
```

##### Links
- this document: [https://landeco.umass.edu/web/massmarsh/flight_data_summary.html](https://landeco.umass.edu/web/massmarsh/flight_data_summary.html)
- Field data summary: [https://landeco.umass.edu/web/massmarsh/field_data_summary.html](https://landeco.umass.edu/web/massmarsh/field_data_summary.html)


### Flight goals for U-Net
- We want to match good years of field data with a rich set of flights. Focus on ortho:mica and DEM at low (or mid) tide, multiple seasons.




# OTH (Old Town Hill)

```{r}
flightinfo('oth')
```

### Notes
- Active management at this site
- Have field data for 2018 and 2021 look reasonably promising (except for mowing in the high marsh). 2025 has a decent sample, but is 
  inadequate orthos.
- Flights for 2018 are inadequate
- Flights for 2021 look iffy
- Flights for 2025 are inadequate


# PEG (Peggotty Beach)

```{r}
flightinfo('peg')
```

### Notes


# SOR (South River)

```{r}
flightinfo('sor')
```

### Notes


# NOR (North River)

```{r}
flightinfo('nor')
```

### Notes
- We have a crazy amount of field data for 2019, 2023, and 2025 at this site


# WEL (Wellfleet Bay)

```{r}
flightinfo('wel')
```

### Notes
- Field data at this site looks great for 2019, and perhaps promising for 2025 (though no orthos). Inadequate for 2023.


# RR (Red River)

```{r}
flightinfo('rr')
```

### Notes
- Field data might be enough for 2019. 


# ESS (Essex Bay)

```{r}
#flightinfo('ess')
```

### Notes
- Active management at this site
- No field data yet


# BAR (Barnstable)

```{r}
flightinfo('bar')
```

### Notes
- No field data yet


# WES (Westport)

```{r}
flightinfo('wes')
```

### Notes
- No field data yet






